\textit{Supplemental materials for:} High-order cognition is supported by information-rich but compressible brain activity patterns

### 2023-03-15 paper/main.tex
starting to add material to supplement, also added new figure to main text and removed the old neurosynth figures

\newcommand{\synthThirds}{S1}
\newcommand{\accuracyNetworks}{S2}
\newcommand{\componentsNetworks}{S3}

@@

\begin{figure}[tp]
  \centering
  \includegraphics[width=\textwidth]{figs/pca_neurosynth}

\caption{\textbf{Top terms associated with the highest-weighted components by
condition.} Each row corresponds to an experimental condition, and the colors
correspond to the component number (ranked by proportion of variance
explained). The inflated brain plots display the top 20 highest-weighted hubs
(see \textit{Topographic Factor Analysis}) for each components'. The lists on
the right display the top five Neurosynth terms~\citep{RubiEtal17} decoded from
each components' brain map. Analogous maps computed separately for each story
segment may be found in Figure~\synthThirds.}

@@

@@

We examined fMRI data collected as participants listened to an auditory
recording of a story, scrambled recordings of the story, or underwent a resting
state scan. We found that cognitively richer stimuli evoked more reliable
(i.e., consistent across people) and information rich brain activity patterns.
The brain patterns evoked by cognitively richer stimuli were also more
compressible, in that each individual component provided more ``signal'' to
temporal decoders relative to components of data from less cognitively rich
conditions (Fig.~\ref{fig:inflection}). Over time (e.g., as the experiment
progressed), these phenomena were strengthened. Specifically, across story
segments, data from more cognitively rich conditions became more informative
and compressible, and data from less cognitively rich conditions became
\textit{less} informative and compressible (Fig.~\ref{fig:inflection-thirds}).
We also repeated these analyses separately for different brain networks. We
found that networks traditionally associated with higher-level cognitive
functions tended to provide more informative brain patterns than networks
traditionally associated with lower level cognitive functions
(Fig.~\ref{fig:networks}). Finally, we examined the most dominant components of
the brain activity patterns from each experimental condition. We used a reverse
inference approach~\citep{RubiEtal17} to identify the terms in the neuroimaging
literature most commonly associated with the corresponding maps. As summarized
in Figure~\ref{fig:discussion}, we found that terms associated with memory and
sensory processing were associated with the strongest components in all three
story listening conditions. Terms associated with sensory integration were
associated with the strongest components in the intact and paragraph-scrambled
conditions. Terms associated with sentence comprehension, emotion, and valence
were associated with the strongest components in the intact condition. Finally,
terms associated with the default mode network were associated with the
strongest components in the word-scrambled and resting state conditions. Taken
together, our findings indicate that the informativeness and compressibility of
our brain activity patterns are task-dependent, and these properties change
systematically with factors like cognitive richness and depth of processing.

\begin{figure}[tp]
  \centering
  \includegraphics[width=\textwidth]{figs/discussion}

\caption{\textbf{Summary of functions associated with top-weighted components
by condition.} Each column corresponds to an experimental condition. Brain maps
in the top row are reproduced from Figure~\ref{fig:neurosynth-pca}, for
reference. Cognitive functions summarized from the top Neurosynth-derived terms
in Figure~\ref{fig:neurosynth-pca} are listed in the rows on the left.  Shaded cells
denote which experimental conditions were associated with one or more top-weighted
principal components associated with the given function.}

\label{fig:discussion}
\end{figure}

>>>>

\newcommand{\synthThirds}{S1}
\newcommand{\accuracyNetworks}{S2}
\newcommand{\componentsNetworks}{S3}
\newcommand{\componentBrains}{S4}
\newcommand{\topTerms}{S5}

\newcommand{\topics}{S1}

@@

\begin{figure}[tp]
  \centering
  \includegraphics[width=\textwidth]{figs/neurosynth_by_component}

\caption{\textbf{Neurosynth topic weightings by component.} We used a reverse
inference procedure (see \textit{Reverse inference}) to estimate the
correspondences between brain images and a set of 80 topics derived from the
Neurosynth database of neuroimaging articles~\citep{RubiEtal17}. \textbf{A.
Topic correlations by component.} For each of the top five highest-weighted
principal components (columns) derived from each experimental condition
(colors), the radar plots display the correlations between the component images
and the per-topic images derived for each topic (topic identities are denoted
by the blue dots; a legend for the topic labels is in the lower right of the
figure). The top-weighted terms for each topic may be found in Table~\topics.
\textbf{B. Topic correlations averaged across components.} The radar plot is in
the same format as the plots in Panel A, but here we display the per-condition
average correlations across the top five components (for each condition)
reflected in Panel A. \textbf{C. Component images.} Each plot diplays a right
sagittal view of a glass brain projection of the top five principal components
(columns) for each experimental conditions (rows). Additional projections for
each component may be found in Figure~\componentBrains.}

@@

\begin{figure}[tp]
  \centering
  \includegraphics[width=\textwidth]{figs/components_neurosynth_summary}

\caption{\textbf{Summary of functions associated with top-weighted components
by condition.} \textbf{A. Top-weighted topics by condition.} Here we display
per-condition (rows, indicated by colored dots) topic correlations, averaged
across topics that pertain to each of several broad cognitive functions
(columns within each sub-panel, indicated by colored dots). Each sub-panel
reflects correlations for the components indicated in the panel titles. A
legend for the condition and several core cognitive function classifications is
displayed in the lower right of the figure. Table~\topics~provides a list of
each topic's top-weighted terms, along with each topic's manually labeled
cognitive classification. A full list of the topics most highly associated with
each component may be found in Figure~\topTerms. \textbf{B. Associations
between per-condition components and cognitive functions.} The network plots
denote positive average correlations between the component images for each
condition (gray-outlined dots on the left sides of each network; colors denote
conditions) and topic-specific brain maps associated with each indicated
cognitive function (black-outlined dots on the right sides of each network;
colors denote cognitive functions). The line thicknesses are proportional to
the correlation values (correlation coefficients are noted in the heatmaps in
Panel A). \textbf{C. Correlations between each principal component, by
condition.} The heatmaps display the correlations between the brain maps
(Fig.~\componentBrains) for each principal component (sub-panel), across each
pair of conditions (rows and columns of each sub-panel's matrix, indicated by
colored dots). \textbf{D. Associations between per-condition components, by
component.} Each sub-panels network plot summarizes the pattern of correlations
between the $n$\textsuperscript{th} top-weighted principal components
(sub-panel) for each experimental condition (gray-outlined dots). The line
thicknesses are proportional to the correlation values (correlation
coefficients are noted in the heatmaps in Panel C).}

\label{fig:neurosynth-summary}
\end{figure}

@@

We examined fMRI data collected as participants listened to an auditory
recording of a story, scrambled recordings of the story, or underwent a resting
state scan. We found that cognitively richer stimuli evoked more reliable
(i.e., consistent across people) and information rich brain activity patterns.
The brain patterns evoked by cognitively richer stimuli were also more
compressible, in that each individual component provided more ``signal'' to
temporal decoders relative to components of data from less cognitively rich
conditions (Fig.~\ref{fig:inflection}). Over time (e.g., as the experiment
progressed), these phenomena were strengthened. Specifically, across story
segments, data from more cognitively rich conditions became more informative
and compressible, and data from less cognitively rich conditions became
\textit{less} informative and compressible (Fig.~\ref{fig:inflection-thirds}).
We also repeated these analyses separately for different brain networks. We
found that networks traditionally associated with higher-level cognitive
functions tended to provide more informative brain patterns than networks
traditionally associated with lower level cognitive functions
(Fig.~\ref{fig:networks}). Finally, we examined the most dominant components of
the brain activity patterns from each experimental condition. We used a reverse
inference approach~\citep{RubiEtal17} to identify the terms in the neuroimaging
literature most commonly associated with the corresponding maps. As summarized
in Figure~\ref{fig:neurosynth-summary}, we found that terms associated with memory and
sensory processing were associated with the strongest components in all three
story listening conditions. Terms associated with sensory integration were
associated with the strongest components in the intact and paragraph-scrambled
conditions. Terms associated with sentence comprehension, emotion, and valence
were associated with the strongest components in the intact condition. Finally,
terms associated with the default mode network were associated with the
strongest components in the word-scrambled and resting state conditions. Taken
together, our findings indicate that the informativeness and compressibility of
our brain activity patterns are task-dependent, and these properties change
systematically with factors like cognitive richness and depth of processing.

### 2023-03-15 paper/supplement.tex
applied a coat of polish to the text-- fixed a bunch of minor issues throughout (mostly typos).  i also corrected some errors in figure 1.
backing up progress on neurosynth analyses
starting to add material to supplement, also added new figure to main text and removed the old neurosynth figures

\documentclass[english]{article}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{setspace}
\usepackage{apacite}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage{pxfonts}
\usepackage[utf8]{inputenc}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage[left]{lineno}
\usepackage{soul}
\linenumbers

\newcommand{\synth}{1}
\renewcommand{\thefigure}{S\arabic{figure}}

\title{\textit{Supplemental materials for:} High-order cognition is supported by complex but compressible brain activity patterns}

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/pca_neurosynth_thirds}

\caption{\textbf{Top terms associated with the highest-weighted components by
condition, broken down by story segment.} Each group of three rows corresponds
to an experimental condition, and the colors correspond to the component number
(ranked by proportion of variance explained). The rows' numbering denotes the
story segment used to compute each map (1: first third; 2: second third; 3:
third third). The inflated brain plots display the top 20 highest-weighted hubs
(see \textit{Topographic Factor Analysis}) for each components. The lists on
the right display the top five Neurosynth terms~\citep{RubiEtal17} decoded from
each components' brain map. Analogous maps computed for the entire story may be
found in Figure~\synth.}

\label{fig:neurosynth-thirds}

>>>>

\documentclass[english]{article}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{setspace}
\usepackage{apacite}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage{pxfonts}
\usepackage[utf8]{inputenc}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage[left]{lineno}
\usepackage{soul}
\usepackage[table]{xcolor}
\usepackage{colortbl}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{rotating}
\usepackage{supertabular}

\linenumbers

\newcommand{\synth}{1}
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thetable}{S\arabic{table}}

\title{\textit{Supplemental materials for:} High-order cognition is supported by information-rich but compressible brain activity patterns}

@@

% \begin{figure}
%   \centering
%   \includegraphics[width=\textwidth]{figs/pca_neurosynth_thirds}

% \caption{\textbf{Top terms associated with the highest-weighted components by
% condition, broken down by story segment.} Each group of three rows corresponds
% to an experimental condition, and the colors correspond to the component number
% (ranked by proportion of variance explained). The rows' numbering denotes the
% story segment used to compute each map (1: first third; 2: second third; 3:
% third third). The inflated brain plots display the top 20 highest-weighted hubs
% (see \textit{Topographic Factor Analysis}) for each components. The lists on
% the right display the top five Neurosynth terms~\citep{RubiEtal17} decoded from
% each components' brain map. Analogous maps computed for the entire story may be
% found in Figure~\synth.}

% \label{fig:neurosynth-thirds}

% \end{figure}

\begin{landscape}
  \tablehead{\toprule
  Topic label &     Cognitive label &           Term 1 &        Term 2 &          Term 3 &         Term 4 &      Term 5 &         Term 6 &        Term 7 &         Term 8 &        Term 9 &        Term 10 \\
  \midrule
  }
  \tabletail{\bottomrule}
  \tiny

\begin{supertabular}{rlllllllllll}
  Cognitive control and task performance &   Cognitive control &            tasks &       control &         network &     conditions &  comparison &      performed &        common &     correlates &    experiment &            pre \\
  Developmental aging and maturation &                   - &              age &        adults &        children &    development & adolescents &          aging & developmental &    adolescence &     childhood &          adult \\
  Eye movements and visual attention &           Attention &              eye &          gaze &            eyes &         visual &    saccades &      movements &       saccade &      direction &          gait &         target \\
        Facial and voice recognition &  Sensory perception &      recognition &      familiar &        identity &     unfamiliar &       voice &    familiarity &         route &         voices &            fg &         facial \\
Social interaction and contextual behavior &    Social cognition &          context &          game &           human &    interaction &         ppi &     contextual &      contexts &         agency &  interactions &        partner \\
Language processing and semantic knowledge & Language processing &         semantic &         words &            word &        lexical &      verbal &       language &         tasks &         naming &       fluency &   phonological \\
Experimental design and behavioral performance &                   - &           trials &      stimulus &       responses &          trial &    reaction &           time &         event &         target &        events &          times \\
Genetic polymorphisms and risk factors &                   - &         carriers &        allele &            gene &       genotype &         met &        genetic &  polymorphism &            val &          comt &             rs \\
Sensorimotor integration and movement control &       Motor control &            motor &      movement &       movements &   sensorimotor &     primary &         finger &       control &        imagery &       sensory &      execution \\
  Drug addiction and substance abuse &                   - &          cocaine &         users &            drug &            bpd &    controls &       cannabis &     addiction &        craving &     dependent &         heroin \\
Music perception and auditory processing &  Sensory perception &            music &       musical &           pitch &       auditory &   musicians &      sequences &        rhythm &      listening &          beat &        singing \\
Menstrual cycle and hormonal regulation &                   - &            phase &         women &           cycle &         phases &   menstrual &             hf &    expression &            sex &        luteal &     follicular \\
Cognitive functions and role playing &   Cognitive control &             role &          play &           human &          plays &   cognitive &       evidence &      critical &       distinct &           key &     subregions \\
   Inhibition and gender differences &                   - &       inhibition &         women &      inhibitory &            sex &     females &         gender &         males &           stop &          male &         female \\
Somatosensory stimulation and motor control &       Motor control &      stimulation & somatosensory &             tms &        tactile &     primary &          touch &         motor &           rtms &  transcranial &        sensory \\
Multisensory integration and perception &  Sensory perception &         auditory &        visual &         sensory &       modality &      sounds &    integration &         sound &       stimulus &       primary &     modalities \\
       Social perception and empathy &    Social cognition &           social &       empathy &      experience &         people &      person &      responses &   perspective &    individuals &    attachment &       empathic \\
Gesture recognition and visual attention &           Attention &           target &      gestures &         targets &    orientation &      visual &    distractors &       gesture &          grasp &    distractor &       location \\
                 Experimental design &                   - &           design &         block &          blocks &          event &       mixed &      condition &            ca &        writing &       blocked &           runs \\
              Alcohol cue reactivity &              Reward &             cues &           cue &         alcohol &   anticipation &        cued &    preparation &  anticipatory &       exposure &    expectancy &    preparatory \\
         Neuroimaging and metabolism &                   - &              pet &    tomography &        emission &       positron &        flow &        glucose &       binding &     metabolism &     metabolic &       receptor \\
      Abnormalities in schizophrenia &                   - &    schizophrenia &      controls &         reduced &  abnormalities &    symptoms &       deficits &       matched &        control &      abnormal &  schizophrenic \\
              Eating and body weight &                   - &             food &         taste &            body &         weight &      eating &          women &         obese &         reward &         foods &        caloric \\
      Sleep and olfactory processing &  Sensory perception &            sleep &     olfactory &            odor &             sd & deprivation &          odors &           rem &    wakefulness &         night &           wake \\
Alzheimer's disease and mild cognitive impairment &                   - &               ad &       disease &             mci &      alzheimer &   cognitive &     impairment &          mild &           amci &      controls &        atrophy \\
Working memory and executive function &              Memory &           memory &          load &           tasks &         verbal & maintenance &    performance &          term &     difficulty &          dual &      cognitive \\
   Moral decision making and phobias &                   - &            moral &        phobia &          phobic &             ec &       guilt &         spider &      decision &            art &       phobics &    intentional \\
                 Language laterality & Language processing &         language &     asymmetry &    organization &          human &   dominance &    asymmetries &   lateralized &         handed &       located & representation \\
                           Attention &           Attention &        attention &   attentional &          visual &        spatial &         top &      selective &      stimulus &        control &     orienting &         target \\
Resting-state brain activity in smokers &       Resting state &             reho &       smokers &         resting &        smoking &    nicotine &    homogeneity &           sci &       controls &            rs &    spontaneous \\
           Social cognition/judgment &    Social cognition &           social &     judgments &            mind &         mental &      theory &    mentalizing &     cognition &       judgment &        person &         people \\
          Reward and decision making &              Reward &           reward &      decision &          choice &       outcomes &     rewards &       monetary &     decisions &   anticipation &     responses &        outcome \\
         ADHD and attention deficits &           Attention &             adhd &      disorder &       attention &        deficit &    children &  hyperactivity &      deficits &        control &      controls &        reduced \\
Neurobiological variability and individual diff... &                   - &       individual &  relationship &           local &      dependent &      change &         global &     responses &       neuronal &     magnitude &          lower \\
                   Spatial cognition &   Spatial cognition &          spatial &         space &        location &      locations &  navigation &        virtual &        visual &   visuospatial &         visuo &       position \\
Therapeutic interventions and training &                   - &         training &   acupuncture &         therapy &             cr &     control &        trained &   improvement &    mindfulness &   stimulation &        induced \\
      Color perception and deception &  Sensory perception &            color &        search &         feature &      deception &    features &      responses &        colour &      dimension &         lying &    conjunction \\
Neurodegenerative diseases and disorders &                   - &          disease &            pd &        controls &        atrophy &    clinical &          motor &      dementia &             sd &      multiple &      sclerosis \\
  Cognitive control and interference &   Cognitive control &         conflict &       control &    interference &         stroop & incongruent &      selection &     congruent &         trials &     cognitive &     monitoring \\
Structural MRI and brain volume analysis &                   - &           volume &          gray &           voxel &             gm & morphometry &           grey &       volumes &            vbm &       density &            age \\
    Fear conditioning and extinction &             Emotion &             fear &     switching &    conditioning &      responses &    stimulus &     extinction &            cs &         switch &        threat &    conditioned \\
        Skill learning and expertise &              Memory &         learning &      practice &         learned &       sequence & performance &       training &     sequences &          skill &      implicit &          motor \\
                     PTSD and trauma &             Emotion &             ptsd &        trauma &          stress &       disorder &   traumatic &  posttraumatic &     childhood &      survivors &      exposure &       controls \\
Neural oscillations and electrophysiology &                   - &        frequency &        source &           alpha &      amplitude &        beta &          gamma &      recorded &    frequencies &     potential &   simultaneous \\
Temporal dynamics of stimulus processing &  Sensory perception &             time &     sustained &        duration &          onset &      period &          stage &        timing &          delay &     transient &          event \\
           Tinnitus and hearing loss &  Sensory perception &         tinnitus &          loss &         hearing &         status &     driving &     subjective &     objective &         unfair &        offers &      rejection \\
Abstract categories and representations & Language processing &         category &    adaptation & representations & categorization &  categories &       abstract &      stimulus & representation &      features &      knowledge \\
Pain perception and sensory stimulation &  Sensory perception &             pain &       painful &     stimulation &  somatosensory &   intensity &        noxious &          heat &        chronic &       sensory &    nociceptive \\
                   Body and primates &                   - &             body &         human &          humans &        monkeys &        itch &       primates &       species &         monkey &        bodies &        macaque \\
  Phonological processing in reading & Language processing &          reading &       chinese &    phonological &         visual &    language &        readers &      dyslexia &     characters &      children &           word \\
Rule-based performance and complexity &   Cognitive control &             rule &    complexity &            size &          force &       rules &         effect &          grip &         amount &      distance &     artificial \\
Autism Spectrum Disorder (ASD) and social impai... &    Social cognition &              asd &        autism &          social &       spectrum & individuals &       controls &     disorders &       children &            td &        reduced \\
Major depression disorder and emotions &             Emotion &       depression &           mdd &       depressed &     depressive &       major &           mood &      disorder &            sad &      controls &        control \\
                Blindness and vision &  Sensory perception &            blind &        visual &         sighted &    individuals &       humor &       laughter &  congenitally &      blindness &    plasticity &        braille \\
          Deafness and sign language & Language processing &        condition &    conditions &            deaf &        hearing &        sign &          signs &   referential &        signers &            ci &            nss \\
Genetic risk and familial factors in psychosis &                   - &             risk &       genetic &              sz &       siblings &   relatives &    individuals &    unaffected &        factors &        family &      psychosis \\
    Action observation and imitation &       Motor control &           action &       actions &     observation &          motor &      mirror &           goal &     imitation &      execution &      directed &      movements \\
   Cognitive performance and control &   Cognitive control &      performance &     cognitive &         control &         memory &   executive &           test &         tasks &    individuals &    behavioral &       deficits \\
       Mental disorders and controls &                   - &         disorder &           ocd &         bipolar &             hc &          bd &       controls &            ts &        control & abnormalities &     compulsive \\
Pharmacological effects of placebo and drug adm... &                   - &          placebo &      dopamine &          effect &           drug &          ht & administration &         blind &   dopaminergic &        double &             mg \\
             Personality and anxiety &    Social cognition &          anxiety &   personality &           trait &    individuals &      scores &         traits &        threat &      disorders &        social &      avoidance \\
   Mental imagery and math abilities &   Cognitive control &           mental &       imagery &       numerical &     arithmetic &    rotation &    calculation &     magnitude &          digit &         tasks &   mathematical \\
       Priming and repetition effect &              Memory &          priming &    repetition &     suppression &       repeated &      effect &       implicit &       literal &         target &         prime &      metaphors \\
 Working memory and error monitoring &              Memory &               wm &         error &          errors &     prediction & performance &        correct &    monitoring &            ltm &      feedback &      predicted \\
   Sentence comprehension and syntax & Language processing &        sentences &      language &        sentence &  comprehension &   syntactic &       semantic &         verbs &           verb &          word &        meaning \\
              Resting state networks &       Resting state &          network &       resting &         default &           mode &        rest &      intrinsic &     cognitive &   correlations &          seed &    spontaneous \\
Episodic memory encoding and retrieval &              Memory &           memory &      encoding &       retrieval &    recognition &    episodic &          items &    successful &     subsequent &  recollection &         recall \\
           Visual object recognition &  Sensory perception &           object &        visual &         objects &          shape &      images &         scenes &         scene &      selective &   recognition &         stream \\
Effective causal modeling of neural networks &                   - &        effective &        causal &        modeling &        dynamic &     network &            top &     influence &     modulation &  interactions &      causality \\
Relational reasoning and fluid intelligence &                   - &        reasoning &         FALSE &            TRUE &   intelligence &  relational &         belief &     relations &      nonverbal &         fluid &     analogical \\
    Lesion and stroke rehabilitation &                   - &          lesions &        lesion &          stroke &         damage &      injury &       controls &      recovery &        patient &        tracts &      integrity \\
Affective valence and feedback processing &                   - &         negative &      positive &        feedback &        valence &     arousal &           bias &    positively &     negatively &    evaluation &     swallowing \\
 Autobiographical memory in epilepsy &              Memory & autobiographical &        events &          future &       epilepsy &    episodic &         memory &      memories &           past &          mtle &       personal \\
Evidence and effect in behavioral studies &                   - &         evidence &       provide &          effect &     behavioral &  underlying &   demonstrated & understanding &      potential &     responses &        support \\
  Stress and physiological responses &                   - &           stress &          tdcs &        cortisol &      autonomic &       heart &      responses &          rate &     regulation & physiological &        induced \\
      Speech and language processing & Language processing &           speech &      language &        auditory &     production &  perception &  comprehension &     listening &       acoustic &    linguistic &        prosody \\
Network interactions and evidence in human systems &                   - &          network &      evidence &           human &        systems &     support &        process &      distinct &    integration &       provide &        engaged \\
             Neuroimaging techniques &                   - &         standard &        images &      individual &           time &       image &          voxel &       spatial &           test &      clinical &        mapping \\
Visual perception of motion and form &  Sensory perception &           motion &        visual &      perception &     perceptual &  biological &        dynamic &        moving &          human &        static &       illusion \\
 Emotional processing and regulation &             Emotion &        emotional &       emotion &         neutral &         facial & expressions &      affective &     responses &       negative &    regulation &       emotions \\

\end{supertabular}

\caption{\vspace{0.2cm} \normalsize \noindent Table S1: \textbf{Neurosynth-derived topics.} We report the top-weighted terms
for each of 80 topics identified using Latent Dirichlet
Allocation~\citep{BleiEtal03} applied to 9,204 functional neuroimaging articles
in the Neurosynth database~\citep{RubiEtal17}. The topics, as well as
associated brain maps identified using Neurosynth, were identified and reported
in several prior studies~\citep{FoxEtal14, SulEtal17, ChenEtal20}. The topic
labels for each topic were generated automatically with the following ChatGPT
(chat.openai.com) prompt: ``Please help me come up with intuitive labels for
topic topics I found by fitting a topic model to thousands of neuroscience and
psychology articles. I'll paste in the top 10 highest-weighted words for each
topic, and I'd like you to respond with a suggested label. For each topic,
please respond with just the topic label and no other formatting or text. Here
are the next topic's top words:'' followed by a comma-separated list of the
given topic's top-weighted words reflected in the table. For some topics,
ChatGPT responded with a longer-form response rather than a concise topic
label. In these instances, on a case-by-case basis, we used a second follow-up
prompt to achieve the given topic's label: ``could you please come up with a
more concise label for that topic?''. We then manually identified a set of 11
cognitive labels that were intended to encapsulate a representative range of
widely studied low-level and high-level cognitive functions. In choosing the
set of cognitive labels, we jointly considered each topic's ChatGPT-derived
topic label, along with the top-weighted words for the topic. We attempted to
generate a concise set of labels that still spanned the full set of cognitive
functions reflected across the 80 topics. Topics that appeared unrelated to
specific cognitive functions (e.g., topics related to specific methods or
clinical themes) are designated with dashes.

\label{tab:topics}}

\end{landscape}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/top_terms_by_component}

\caption{\textbf{Top terms associated with the highest-weighted components by
condition, broken down by story segment.} Each group of five rows corresponds
to an experimental condition (denoted by color, as indicated in the legend in
the lower right), and the columns and shading correspond to the component
number (ranked by proportion of variance explained). The colored squares in
front of many of the topics denote manually identified cognitive labels
(Tab.~S1).}

\label{fig:top-terms}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/topic_contrasts}

\caption{\textbf{Fill this in...}}

\label{fig:contrasts}
